|

### 2024-10-15 posts/BarthPapageorgeThom/BPT.qmd
Completed BPT.html for RG2024/10/15

:::{.fragment}
Gradient: "ability" + school quality &larr; income measure error
:::
:::

@@

* Previous studies: EA scores $\SIM$ education
* This study: EA scores $\SIM$ wealth
* EA scores $\SIM$ probabilistic thinking &rArr; human capital accumulation heterogeneity  
   * Teaching probability may make human capital more homogenous?
   * Not necessarily, gene-wealth gradient is a biased estimate &larr; environment
   * But it hints something can be done there

>>>>

:::{.fragment}
Gradient: "savvy" + school quality &larr; income meas errors
:::
:::

@@

* Previous studies: EA scores $\SIM$ education
* This study: EA scores $\SIM$ wealth|education, parents
* EA scores $\SIM$ probabilistic thinking &rArr; human capital accumulation heterogeneity  
   * Teaching probability may make human capital more homogenous?
   * Not necessarily, gene-wealth gradient is a biased estimate &larr; environment
   * But it hints something can be done there
